### 2022-08-24 manuscript.Rmd
Refactor TFR plotting function

# Define Bonferroni-corrected cluster-level p value threshold
p_cluster <- 0.05 / length(unique(clusters$contrast))
```

@@

```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)", include=TRUE}
# Create topographic plots for event-related power in each phase
tfr_plots <- plot_fig2(
  tfr_grand_ave, tfr_clusters, p_cluster, channel_locations
)

# Plot Pre-Insight Phase
tfr_plots[[1]]
```

@@

```{r, fig3, fig.height=11, fig.cap="(ref:figure-3-caption)", include=TRUE}
# Plot Insight Phase
tfr_plots[[2]]
```

@@

```{r, fig4, fig.height=11, fig.cap="(ref:figure-4-caption)", include=TRUE}
# Plot Post-Insight Phase
tfr_plots[[3]]
```

>>>>

# Define cluster-level p value threshold
p_cluster <- 0.05 / 3 # Bonferroni-corrected for three phases
```

@@

```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)", include=TRUE, eval=TRUE}
# Create topographic plots for event-related power in the pre-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive"),
  p_cluster = p_cluster
)
```

@@

```{r, fig3, fig.height=11, fig.cap="(ref:figure-3-caption)", include=TRUE, eval=TRUE}
# Create topographic plots for event-related power in the insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive"),
  p_cluster = p_cluster
)
```

@@

```{r, fig4, fig.height=11, fig.cap="(ref:figure-4-caption)", include=TRUE, eval=TRUE}
# Create topographic plots for event-related power in the post-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(
    tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive"
  ),
  p_cluster = p_cluster
)
```
